Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-16 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd
#105

$Rt$ had a significantly negative response to $ln[TWI]$ in all drought years combined and in 1977, and a negative effect of $ln[TWI]$ was included in some of the models in 1999 and the $Rt_{ARIMA}$ model for 1966 (Fig. 4, Tables 4-5).
This negates the idea that trees in moist microsites would be less affected by drought. 
Nevertheless, we tested for a negative $ln[H] *ln[TWI]$ interaction, which could indicate that smaller trees (with smaller rooting volume) are more susceptible to drought in drier microenvironments with a deeper water table. 
This hypothesis was rejected, as the $ln[H] *ln[TWI]$ interaction was never the significant, and had a positive sign in any top models  in which it appeared (Tables 1, S6-S7).
This term did appear, with positive coefficient, in the best $Rt_{ARIMA}$ model for all years combined (Table S7).

>>>>

$Rt$ had a significantly negative response to $ln[TWI]$ in all drought years combined and in 1977, and a negative effect of $ln[TWI]$ was included in some of the models in 1999 and the $Rt_{ARIMA}$ model for 1966 (Fig. 4, Tables 4-5).
This negates the idea that trees in moist microsites would be less affected by drought. 
Nevertheless, we tested for a $ln[H] *ln[TWI]$ interaction, a negative sign of which could indicate that smaller trees (with smaller rooting volume) are more susceptible to drought in drier microenvironments with a deeper water table. 
This hypothesis was rejected, as the $ln[H] *ln[TWI]$ interaction was never significant, and had a positive sign in any top models  in which it appeared (Tables 1, S6-S7).
This term did appear, with positive coefficient, in the best $Rt_{ARIMA}$ model for all years combined (Table S7).
